---
title: "XX"
author: "Umaira"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```
Immigration attitudes among voters remain a contentious political issue, with exposure to different groups potentially shaping public opinion on immigration policy. Using data from a 2016 experiment conducted on train platforms in Georgia with 115 registered voters, we examine whether exposure to Spanish-speakers causally affects attitudes toward immigration.One potential weakness of our model is that it assumes a linear relationship and no omitted variable bias, which may not hold if other unmeasured factors also influence immigration attitudes.
We model attitudes toward immigration, measured on a continuous scale, as a linear function of whether or not the respondent was exposed to Spanish speakers on a train platform.

$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$.


$$
\hat{\text{att\_end}} = 8.45 + 1.45 \cdot \text{treatment}
$$


```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |>
  fit(att_end ~ treatment, data = trains)
```


```{r}
#| label: tbl-fit-att
#| echo: false
#| message: false
#| warning: false

fit_att |>
  tidy(conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  gt() |>
  tab_header(
    title = "Estimated Effect of Treatment on Attitudes"
  ) |>
  cols_label(
    term = "Variable",
    estimate = "Estimate",
    conf.low = "Lower 95% CI",
    conf.high = "Upper 95% CI"
  ) |>
  fmt_number(columns = c(estimate, conf.low, conf.high), decimals = 2)
```


```{r}
#| label: plot-treatment-effect
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(marginaleffects)

# Get average comparison (treatment effect)
avg_eff <- avg_comparisons(fit_att)

# Plot it
ggplot(avg_eff, aes(x = term, y = estimate)) +
  geom_point(size = 4, color = "#0072B2") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2, color = "#0072B2") +
  labs(
    title = "Effect of Exposure to Spanish Speakers on Immigration Attitudes",
    subtitle = "Those exposed to Spanish speakers became more conservative by ~1.55 points, on average",
    x = "Treatment",
    y = "Estimated Effect on Immigration Attitude (att_end)",
    caption = "Data: 2012 experiment by Ryan Enos on Boston commuters"
  ) +
  theme_minimal(base_size = 13)
```

On average, exposure to Spanish speakers increased conservative attitudes toward immigration by 1.55 points, with a 95% confidence interval ranging from 0.51 to 2.58, suggesting a meaningful and statistically significant effect.Given these concerns, a more conservative estimate might be that brief exposure to Spanish speakers makes voters somewhat more conservative on immigration, by approximately 0.8 to 2.2 units (with a wider confidence interval of ±0.7 to ±2.0), acknowledging that this effect may vary substantially across different voter populations and real-world contexts. This reflects greater uncertainty about both the magnitude and generalizability of the observed effect.
