---
title: "XX"
author: "Umaira"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
```
Immigration attitudes among voters remain a contentious political issue, with exposure to different groups potentially shaping public opinion on immigration policy. Using data from a 2016 experiment conducted on train platforms in Georgia with 115 registered voters, we examine whether exposure to Spanish-speakers causally affects attitudes toward immigration.One potential weakness of our model is that it assumes a linear relationship and no omitted variable bias, which may not hold if other unmeasured factors also influence immigration attitudes.

$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$.


$$
\hat{\text{att\_end}} = 8.45 + 1.45 \cdot \text{treatment}
$$


```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |>
  fit(att_end ~ treatment, data = trains)
```
